---
title: "Network analysis - Final Project"
author: "Julius Rissanen"
date: "4 toukokuuta 2017"
output: html_document
---
#Financial stability


Banking connectedness?

Traditional stress testing based on simulation on different scenarios. Commonplace after 2007 financial crisis

"A stress test, in financial terminology, is an analysis or simulation designed to determine the ability of a given financial instrument or financial institution to deal with an economic crisis. Instead of doing financial projection on a "best estimate" basis, a company or its regulators may do stress testing where they look at how robust a financial instrument is in certain crashes, a form of scenario analysis." -Wikipedia

Only microprudential analysis. Macroprudential analysis? -> Network analysis

##Some literature

http://www.elibrary.imf.org/staticfiles/misc/toolkit/pdf/chap13.pdf
http://www.bankofengland.co.uk/research/Documents/ccbs/whfs16/presentation_rajagopal.pdf
https://www.ecb.europa.eu/pub/pdf/other/modellingsystemicrisk012010en.pdf

#Dataset

Problematic for individual

Access only for aggregates:
http://stats.bis.org/statx/srs/table/b4

#Analysis

```{r, message =F}
library(igraph)
library(dplyr)
library(GGally)
library(Hmisc)
```

```{r}

setwd("C:/Users/Julius/yliopisto/kansis/datascience/network_analysis/final-project/SNA/")


bank <- read.csv("immediaterisk_clean.csv", sep = ";", dec = ",", row.names = 1)
head(bank, n=2)
str(bank)
bank


keep_columns <- c("Austria", "Belgium", "Finland", "France", "Germany", "Greece", "Ireland", "Italy", "Netherlands","Spain")
bank_eu <- select(bank, one_of(keep_columns))
bank_eu <- bank_eu[c(2,3,8,9,10,11,12,13,17,19),]
bank[is.na(bank)] <- 0
bank_eu[is.na(bank_eu)] <- 0
bank_eu

matrix_eu <- as.matrix(bank_eu)
matrix <- as.matrix(bank)


g <- graph_from_adjacency_matrix(matrix, 'directed',  weighted = T)
g_eu <- graph_from_adjacency_matrix(matrix_eu, 'directed',  weighted = T)

plot(g, edge.width = log(graph.strength(g)*0.001), edge.arrow.mode = 0, layout = layout_with_fr)

plot(g_eu, edge.width = log(E(g_eu)$weight*0.04), edge.arrow.mode = 0)
```








http://kateto.net/networks-r-igraph
